---
title: "p8105_hw1_aar2192.Rmd"
author: "Amadeia Rector"
date: "9/18/2018"
output: github_document
---
This is homework 1 

# Problem 1

Here's a **code chunk** that samples from a _uniform[0, 5] distribution_:

```{r uniform_distribution}
library(tidyverse)
set.seed(1234)

size10_df = tibble(
  unif_sample = runif(10, 0, 5),
  log_vec_gr2 = c("unif_sample" > 2),
  char_vec_ln10 = c("I", "do", "not", "know", "what", "I", "am", "doing", "right", "now"),
  fact_vec_ln10 = factor(c("one", "two", "three", "one", "one", "three", "two", "two", "two", "three"))
)
```

## Taking the mean of log_vec_gr2

```{r mean_log_vec_gr2, results='hide'}
mean(size10_df$log_vec_gr2)
```
The mean of log_vec_gr2 is `r mean(size10_df$log_vec_gr2)`

While I get a result,this doesn't really make sense as there shouldn't be numerical values attached to a logical vector. In this case the logical vector has been interpreted as numerical, with "TRUE" meaning "1" and "FALSE" meaning "0"

## Taking the mean of char_vec_ln10

```{r mean_char_vec_10, results='hide', warning=FALSE}
mean(size10_df$char_vec_ln10)
```
The returned result is a warning message and a returned missing value, NA.

We cannot obtain the mean of a character vector, as it is not numeric.

## Taking the mean of fact_vec_ln10

```{r mean_fact_vec_ln10, results='hide', warning=FALSE}
mean(size10_df$fact_vec_ln10)
```
The returned result is a warning message and a returned missing value, NA.

We cannot obtain the mean of a factor vector, as it is not numeric.

## Converting the variables into numeric values

```{r convert_numeric, results='hide', warning=FALSE}
as.numeric(size10_df$log_vec_gr2)
as.numeric(size10_df$char_vec_ln10)
as.numeric(size10_df$fact_vec_ln10)
```
The logical vector and the factor vector converts to numeric, but the character vector is unable to do so. Instead, NAs are introduced by coercion for the character vector.

```{r convert_char, results='hide', warning=FALSE}
as.numeric(as.factor(size10_df$char_vec_ln10))
as.numeric(as.character(size10_df$fact_vec_ln10))
```
The character vector that is first turned into a factor variable and then a numeric vector now has numeric values. Specifically, because I used 8 unique words in my characters, the numeric values include numbers 1-8, with 4 repeated two times.
However, the factor vector that is first turned into a character variable and then coerced into numeric gives NA results since a character vector cannot be turned numeric unless it is first turned into a factor.
