---
title: "p8105_hw1_aar2192.Rmd"
author: "Amadeia Rector"
date: "9/18/2018"
output: github_document
---
This is homework 1 

# Problem 1

Here's a **code chunk** that samples from a _uniform[0, 5] distribution_:

```{r uniform_distribution}
library(tidyverse)
set.seed(1234)

size10_df = tibble(
  unif_sample = runif(10, 0, 5),
  log_vec_gr2 = c("unif_sample" > 2),
  char_vec_ln10 = c("I", "do", "not", "know", "what", "I", "am", "doing", "right", "now"),
  fact_vec_ln10 = factor(c("one", "two", "three", "one", "one", "three", "two", "two", "two", "three"))
)
```

## Taking the mean of log_vec_gr2

```{r mean_log_vec_gr2, results='hide'}
mean(size10_df$log_vec_gr2)
```
The mean of log_vec_gr2 is `r mean(size10_df$log_vec_gr2)`

While I get a result,this doesn't really make sense as there shouldn't be numerical values attached to a logical vector. In this case the logical vector has been interpreted as numerical, with "TRUE" meaning "1" and "FALSE" meaning "0"

## Taking the mean of char_vec_ln10

```{r mean_char_vec_10, results='hide'}
mean(size10_df$char_vec_ln10)
```
The returned result is a warning message and a returned missing value, NA.

We cannot obtain the mean of a character vector, as it is not numeric.

## Taking the mean of fact_vec_ln10

```{r mean_fact_vec_ln10, results='hide'}
mean(size10_df$fact_vec_ln10)
```
The returned result is a warning message and a returned missing value, NA.

We cannot obtain the mean of a factor vector, as it is not numeric.

